Functional Enrichment Tests: Intro and methods comparison

### 2023-06-15 DRAFT_Funct_Enrich.Rmd
Added bibliographic reference on for meta analysis of enrichment studies. Added text on guidelines for rigorous reporting of enrichment analyses.

>>>>

While functional gene enrichment analysis poses many challenges to non-model systems, it is critical the analyses conducted be as rigorous and replicable as possible. A recent survey of published enrichment results indicated that issues in the performance and reporting of enrichment analyses is not uncommon [@RN335]. Basic standards advised by the authors include:

* Selection of appropriate gene background set. This set should not necessarily be the full set of genes in the genome. Rather it should be the set of genes expressed in the experiment. This is especially an issue with overrepresentation analysis and showed a consider impact on results when done incorrectly.
* Multiple hypothesis correction. A common metric used with enrichment results is a false discovery rate (FDR) correction. 
* Adequate methodological reporting including software and parameters used, versions of software and annotation files, all gene lists analyzed including subset and background sets, types of statistical tests and corrections performed, and any code used to conduct the analyses.
